
\begin{itemize} 
\item{}
Our project aims at building a house-buying system for users like house-seekers, landlords, leasing agencies. The recommendation system provides predictions on house's prices according to all the preferences. The system database are built from the website "Weichert", and price prediction is fulfilled using multiple linear regression which ensures the accuracy of the system. Upon using the system interface, users can get the similar houses directly when they move the preference sliders, and it's simple to use.

\begin{enumerate}
\item{}
Title: House buying system(Yi Zhong, Qingqiao Hu, Qi Dong)
\item{}
Project Goal: Building a recommendation system on house sale.
\item{}
Outline of the presentation: 
\item{}
Description: Our project is based on the information from “Weichert”, a website of house renting or buying, and we focus on the houses of New Jersey. We collect the house's information, and save them to our system database. We use linear regression to give prediction to the house price according to the preferences provided by users, and provide the concrete property information of houses for users to choose from. 
 √
\item{}
Pictures are included in stage 4.
\item{}
Project Stumbling Blocks: Information collection, Data processing, Linear Regression, UI Design                                
\item{}
Future Extensions: Expanding the System Database to the US, even the world, Providing more preferences for users to choose from, Building a virtualization of the houses, so that users can get a clear view of similar houses according to the dynamic graph
\item{}
References: Weichert
\end{enumerate}

}